\Huge ACM and Climate Change

### 2019-05-25 main.tex
Fix build

Finally, we can start imposing a cost on ourselves by using carbon
offsets.  
\begin{itemize}
\item There are two good reasons for doing this, as well as some significant
concerns.
\begin{itemize}
\item Reasons in favor:
\begin{itemize}
\item It is the right thing to do: We should be changing our behavior
starting now, and giving ourselves a ``price signal''
\item Offsets reduce carbon emissions now.  (Yes, there are bogus ones, but
not all are bogus.)
\end{itemize}
\item Concerns:
\end{itemize}
\item It is hard to choose the price (right now there is an oversupply), and setting it too low leads to complacency
\item Organizations are not set up to do it.  Our experience with getting
ACM to introduce an offsetting policy shows that it requires significant
effort.
\end{itemize}
People counter-argue that this "lets people off the hook" and
encourages inaction, but we believe it is consistent with encouraging action
-- again, if offsets are priced right.

The climate crisis is too large and too urgent to just delegate to world
leaders: organizations at every social scale must play their part by addressing
their own contributions, raising awareness among their members, and
establishing new ways of 
doing business in the lower-carbon future that is coming. For ACM, this
especially means developing strategies for reducing the climate impact of
conference-related travel.
%
You can help accelerate this process in a number of ways: 
\begin{itemize}
\item {\bf Get involved} in raising awareness about this issue in the
organizations you are a part of.  \bcp{Does this smack of incrementalism?
  Maybe delete it.
  ``For example, ask the organizers of the conferences you attend what they
  are doing about reducing or offsetting emissions from participants'
  travel.''}
\item {\bf Connect} with others that are engaging with these issues---in
your workplace, in your other communities, and within ACM (e.g., on the
{\tt acm-climate} mailing list~\cite{acm-climate}).
\item {\bf Analyze} your organization's carbon-emitting activities to
understand how to reduce its footprint now and prepare for the coming era of
expensive carbon.
\end{itemize}

>>>>

Finally, we can start imposing a cost on ourselves by using carbon
offsets.  
\begin{itemize}
\item There are two good reasons for doing this, as well as some significant
concerns.
\begin{itemize}
\item Reasons in favor:
\begin{itemize}
\item It is the right thing to do: We should be changing our behavior
starting now, and giving ourselves a ``price signal'' is a good way to
achieve this.
\item Offsets reduce carbon emissions now.  (Yes, there are bogus ones, but
not all are bogus.)
\end{itemize}
\item Concerns:
\begin{itemize}
\item 
Organizations are not set up to do it.  Our experience with getting
ACM to introduce an offsetting policy shows that it requires significant
effort.
\item It is hard to choose the price (right now there is an oversupply), and
setting it too low leads to complacency --- it doesn't really bite, so it
doesn't change people's behavior
\end{itemize}
\item People argue that offsets "let people off the hook" and encourage
inaction, but we believe it is consistent with encouraging action -- again,
if offsets are priced right.
\end{itemize}
\end{itemize}

The climate crisis is too large and too urgent to leave it to world leaders
to address at their own pace: organizations at every social scale should
confront their own contributions, raise awareness among their members, and
begin establishing new ways of doing business in the lower-carbon future
that is coming. For ACM, this especially means confronting the
carbon-intensive nature of our conferences.
%
You can help accelerate this process in a number of ways: 
\begin{itemize}
\item {\bf Get involved} in raising awareness about this issue in the
organizations you are a part of.  \bcp{Does the rest of this smack of
  incrementalism?  Maybe delete it.  ``For example, ask the organizers of
  the conferences you attend what they are doing about reducing or
  offsetting emissions from participants' travel.''}
\item {\bf Connect} with others that are engaging with these issues---in
your workplace, in your other communities, and within ACM (e.g., on the
{\tt acm-climate} mailing list~\cite{acm-climate}).
\item {\bf Analyze} your organization's carbon-emitting activities to
understand how to reduce its footprint now and prepare for the coming era of
expensive carbon.
\end{itemize}
